Bayesian Detection of Bias in Peremptory Challenges Using Historical Strike Data

### 2023-02-16 analysis/paper_draft3.Rmd
small edit to intro

Without historical strike data, there is a higher risk of underpowered or inflated estimates of attorney strike bias, because of the low number of strikes per trial: typically from 6 to  15 strikes per party, depending on the jurisdiction [@nscs-jury2018]. Yet, complete pooling of current and historical strike data may be affected by the degree of incompatibility between current and historical strike data. Such incompatibility may occur if missing historical strike is missing not at random due to incomplete or inaccessible jury-selection records [@Grosso2017; @Wright2018].

@@

As a result, for any given estimate of strike bias in a current trial, incompatibility between strike data from that current trial and strike data from past trials can lead to inflated type I error and reduced power [@Bennett2021]. Other methods to increase power may in turn require adjusting for incompatibility implicitly. For example, @Gastwirth2014 [p. 295-297] stratify strike data by trial and apply the Cochran-Mantel-Haenszel test, albeit after first selecting only historical strike data from past trials that are "similar" in their bias-salient characteristics to the current trial [p. 289, 297]. This initial step presumably aims to reduce incompatibility due to variation in those salient characteristics.

>>>>

Without historical strike data, there is a higher risk of underpowered and inflated estimates of attorney strike bias, because of the low number of strikes per trial: typically from 6 to  15 strikes per party, depending on the jurisdiction [@nscs-jury2018]. Yet, complete pooling of current and historical strike data may be affected by the degree of incompatibility between current and historical strike data. Such incompatibility may occur if missing historical strike is missing not at random due to incomplete or inaccessible jury-selection records [@Grosso2017; @Wright2018].

@@

As a result, for any given estimate of strike bias in a current trial, incompatibility between strike data from that current trial and strike data from past trials can lead to inflated type I error and reduced power [@Bennett2021]. Other methods to increase power may in turn require adjusting for incompatibility implicitly. For example, @Gastwirth2014 [p. 295-297] stratify strike data by trial and apply the Cochran-Mantel-Haenszel test, albeit after first selecting only historical strike data from past trials that are "similar" in their bias-salient characteristics to the current trial [p. 289, 297]. This initial step presumably aims to reduce incompatibility due to variation in those salient characteristics. [explain tthat this is something that would need to be disclosed/justified]
